A family of accessibility measures derived from spatial interaction principles

### 2025-04-06 paper/manuscript.qmd
unconstrained access in one step

@@

$$
V^0_{ij} = W_j^{(2)} f(c_{ij})
$$ {#eq-unconstrained-access}

Then, the partial sum becomes the following: simply Hansen's accessibility $S_i$ [@hansen1959], standard practice in accessibility measurement:

@@

unc_acc_ij <- OD |>
  group_by(oid) |>
  reframe(V_unc_ij_1 = D_j * f1,
            V_unc_ij_2 = D_j * f2,
            V_unc_ij_3 = D_j * f3)

unc_acc <- unc_acc_ij |>
  group_by(oid) |>
  summarize(V_unc_i_1 = sum(V_unc_ij_1),
            V_unc_i_2 = sum(V_unc_ij_2),
            V_unc_i_3 = sum(V_unc_ij_3))

>>>>

<!-- this paragraph could probably be merged with the previous one -->

@@

$$
V^0_{ij} = 1 *W_j^{(2)} f(c_{ij})
$$ {#eq-unconstrained-access}

In this case, the partial sum of spatial interaction is simply identical to Hansen's accessibility $S_i$ [@hansen1959], the current standard practice in accessibility measurement:

@@

unc_acc <- OD |>
  group_by(oid) |>
  summarize(V_unc_i_1 = sum(D_j * f1),
            V_unc_i_2 = sum(D_j * f2),
            V_unc_i_3 = sum(D_j * f3))
